%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://electionsbycounty.com/}{\Large Oyedotun Oyesanmi}} &  \href{mailto:dotun@electionsbycounty.com}{dotun@electionsbycounty.com}\\
  \href{https://electionsbycounty.com}{https://electionsbycounty.com} &  574-310-9466 \\
     \href{https://github.com/dotman14}{www.github.com/dotman14} &
  1112 S. 20th str, South Bend, IN, 46614. 
  
  
\end{tabular*}

%-----------EMPLOYMENT-----------------
\section{Employment}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Communications and Marketing - Indiana University South Bend }{South Bend, IN}
      {Web Technician}{July 2016 - May 2017}
      \resumeItemListStart
        \resumeItem{Task}
          {Developed new and managed old IU South Bend using IU Web Framework, many times writing PHP scripts to automate some actions. Hands on experience with Indiana University's range of development platforms.}
      \resumeItemListEnd
      
      \resumeSubheading
      {University Library - Indiana University South Bend }{South Bend, IN}
      {Web Technician}{Sept 2015 - July 2016}
      \resumeItemListStart
        \resumeItem{Apache Beam}
          {Developed new IU South Bend websites and managed old ones using IU Web Framework, many times writing PHP scripts to automate some actions. Hands on experience with Indiana University's range of development platforms.}
      \resumeItemListEnd
      
       \resumeSubheading
      {Admissions Office - Indiana University South Bend }{South Bend, IN}
      {Web Technician}{Feb 2015 - July 2016}
      \resumeItemListStart
        \resumeItem{Apache Beam}
          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and Runners for executing them on distributed processing back ends like Apache Spark, Apache Flink, and Google Cloud Dataflow.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indiana University South Bend}{South Bend, IN}
      {Master of Science in Computer Science;  \comment{GPA: 3.50}}{Jan. 2015 -- May. 2017(Expected)}
     \resumeItemListStart
        \resumeItem{Coursework}
          {Software Engineering, Database Management Systems, Programming in C\#, Data Structures, Computer Security, Calculus, Algorithm Design and Analysis, Parallel and Distributed Computing,  Computer Networks, Game Programming and Design, Data Mining}
      \resumeItemListEnd
    \resumeSubheading
      {Ladoke Akintola University of Technology}{Ogbomoso, Nigeria}
      {Bachelor of Technology in Agricultural Economics and Extension}{Aug. 2005 -- Dec. 2010}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Elections By County}{South Bend, IN}
      {Software Developer}{Nov 2016 - present}
      \resumeItemListStart
        \resumeItem{Project Description: }
          {A simple US elections results management system. Users can view voting trends of their county as far back as 1920. The software also provides a RESTful API for registered users. }\\
          \textbf{Softwares used: }{ASP.NET MVC, Entity Framework, LINQ, Web API, Azure, C\#, Microsoft IIS Server, MSSQL, JavaScript}
      \resumeItemListEnd
      
       \resumeSubheading
      {Simulation Model for IU Ready}{South Bend, IN}
      {Software Developer}{Aug 2016 - May 2017}
      \resumeItemListStart
        \resumeItem{Task}
          {A system to simulate multi-user activities on a web server to benchmark the limits of https://ready.iusb.edu}\\
          \textbf{PHP, MySQL}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Programming Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: ASP.NET MVC, C\#, PHP, SQL}
     \hfill \\
    \item{
    \textbf{Technologies}{: IU Web Framework, Visual Studio, Azure, MySQL, MSSQL, Entity Framework, Web API}
    }}
 \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
